\textbf{Computational Fuzzy Extractors}

### 2013-05-17 CompFuzzExt.tex
worked on section 4.4

\subsection{Comparison with computational-extractor-based constructions}
\label{sec:prg based comparison}
As we already mentioned in the introduction, an alternative approach to building a computational fuzzy extractor is to use  a computational extractor (e.g.,~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational}) in place of the information-theoretic extractor in the sketch-and-extract construction.  We will call this approach \emph{sketch-and-comp-extract}.  (A simple example of a computational extractor is a pseudorandom generator applied to the output of an information-theoretic extractor; but other approaches are also possible.)
%using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.  This is the extract-then-expand computational extractor suggested by Krawczyk in~\cite{krawczyk2010cryptographic}.

This approach (specifically, its analysis via \lemref{lem:fuzzy ext construction}) works as long as the amount of entropy $\tilde{m}$ of $w$ conditioned on the sketch $s$ remains high enough to run a computational extractor.  However, $\tilde{m}$ decreases with the error parameter $t$ due to coding bounds, and it is conceivable that, if $W$ has just barely enough entropy to begin with, it will have too little entropy left to run a computational extractor once $s$ is known.

In contrast, in our approach, the entropy of $w$ conditioned on $p=(\vA, \vA X+w)$ is not relevant to security, because we do not extract from $w$. Instead, we require that $w$ is not recoverable computationally given $p$.  Note that this requirement does not imply that $w$ can be extracted from, because computational extractors may require a longer minimum input length than the computational entropy of $w$.   Our approach works in such a setting because instead of extracting from $w$, we hide secret randomness using $w$.

The main advantage of our analysis (instead of sketch-and-comp-extract) is that security need not depend on the decoding radius $t$.  Our codes (namely, random linear codes) can tolerate very high $t$, in fact.  In the case of secure sketches, codes tolerating such high $t$ would leave little entropy in $w$.  In our construction, the decoding radius depends only on the best available decoding algorithm for random linear codes.

\lnote{use any of the below?}
 utilize secret randomness to obtain the key $r$, and hide that randomness using $w$.

The code defined by $\vA$ can correct very high

Under the same hardness of approximating GAPSVP and SIVP, Applebaum et. al. achieve a pseudorandom generator with linear stretch~\cite{applebaum2006pseudorandom}.  They consider $\vA$ as a public value and show a setting of parameters where $f_\vA(x, e) = \vA x + e$ is a pseudorandom generator with linear stretch.  Likewise, by increasing the field size in \consref{cons:informal construction}, it is possible to output a linear factor of the number of input bits~(see \secref{sec:parameter settings}).  Both techniques are able to produce a linear stretch on the entropy of the source.

Thus, using the same assumptions as \thref{thm:lossless secure conductor log}, we can obtain a computational extractor.  This means we could  build a computational fuzzy extractor using: 1) an information-theoretic secure sketch 2) a computational extractor.
We call the paradigm of running a secure sketch and using a computational extractor \emph{sketch-and-comp-extract}.

Any improvement in computational extractors yields an improvement to the sketch-and-comp-extract construction of a computational fuzzy extractor.  Similarly, a computational fuzzy extractor is also a computational extractor~(ignoring the \rep functionality).  Thus, improving computational fuzzy extractors may improvement computational extractors.

The main advantage to analyzing the construction as a whole~(instead of sketch-and-comp-extract) is that security need not depend on the decoding radius $t$.  In sketch-and-comp-extract paradigm, the computational extractor must be able to handle sources with $\Hoo(W| \sketch(W))$.  As shown in \secref{sec:impossCompSecSketch}, this value depends on bounds from error-correcting codes.  In our construction, the decoding radius does not affect the security of the construction.  The decoding radius only impacts the running time of the decoding algorithm.  Conceivably, a computational fuzzy extractor could be built where only correctness depends on $t$~(not efficiency or security).
%However, the construction of a computational fuzzy extractor by 
%The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log |B_t(\cdot)|)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.  In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.  The work of~\cite{dachman2012computational} shows that these losses in the extract-then-expand construction are in some sense necessary~(the samplable RT conjecture in~\cite{dachman2012computational} has been resolved positively by~\cite{dodis2013key}).

>>>>

\subsection{Comparison with computational-extractor-based constructions}
\label{sec:prg based comparison}
As we already mentioned in the introduction, an alternative approach to building a computational fuzzy extractor is to use  a computational extractor (e.g.,~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational}) in place of the information-theoretic extractor in the sketch-and-extract construction.  We will call this approach \emph{sketch-and-comp-extract}.  (A simple example of a computational extractor is a pseudorandom generator applied to the output of an information-theoretic extractor; note that LWE-based pseudorandom generators exist~\cite{applebaum2006pseudorandom}.)
%using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.  This is the extract-then-expand computational extractor suggested by Krawczyk in~\cite{krawczyk2010cryptographic}.

This approach (specifically, its analysis via \lemref{lem:fuzzy ext construction}) works as long as the amount of entropy $\tilde{m}$ of $w$ conditioned on the sketch $s$ remains high enough to run a computational extractor.  However, as discussed in \secref{sec:impossCompSecSketch}, $\tilde{m}$ decreases with the error parameter $t$ due to coding bounds, and it is conceivable that, if $W$ has  barely enough entropy to begin with, it will have too little entropy left to run a computational extractor once $s$ is known.

In contrast, our approach does not require the entropy of $w$ conditioned on $p=(\vA, \vA X+w)$ to  be high enough for a computational extractor. Instead, we require that $w$ is not computationally recoverable  given $p$.  This requirement is weaker.  The key difference in our approach is that instead of extracting from $w$, we hide secret randomness using $w$. Computational extractors are not allowed to have private randomness \cite[Definition 3]{krawczyk2010cryptographic}.

The main advantage of our analysis (instead of sketch-and-comp-extract) is that security need not depend on the error-tolerance $t$.  Our codes (namely, random linear codes) can tolerate higher $t$ than can be efficiently decoded.  In the case of secure sketches, codes tolerating such high $t$ would leave little entropy in $w$.  In our construction, the error-tolerance depends only on the best available decoding algorithm for random linear codes.

Unfortunately, LWE parameter sizes require relatively long $w$. Therefore, in practice, sketch-then-comp-extract will beat our construction  if the computational extractor is instantiated efficiently based on assumptions other than LWE (for example, a cryptographic hash function for an extractor and a block cipher for a PRG). However, we believe that our conceptual framework can lead to better constructions.  Of particular interest are  other codes that are easy to decode up to $t$ errors but become computationally hard as the number of errors increases.
